Brownian dynamics simulation of cytoplasmic dynein's powerstroke reproduces bidirectional stepping

### 2019-01-12 papers/paper/paper.tex
Make various changes to angle figure to look better, including modifying the cartoon and downsampling one plot

\begin{figure}[tbhp]
  \centering
  \begin{subfigure}[]{0.8\columnwidth}\caption{}\vspace{5pt}\includegraphics[width=\columnwidth]{figures/winch-powerstroke-cartoon}\end{subfigure}\vspace{10pt}\\
  \begin{subfigure}[]{0.5\columnwidth}\caption{}\includegraphics[width=\columnwidth]{../../plots/bothbound_stroke_angles_bd}\end{subfigure}%
  \begin{subfigure}[]{0.5\columnwidth}\caption{}\includegraphics[width=\columnwidth]{../../plots/bothbound_stroke_angles_md}\end{subfigure}\\
  \begin{subfigure}[]{0.5\columnwidth}\caption{}\includegraphics[width=\columnwidth]{../../plots/bothbound_stroke_tailx_positions}\end{subfigure}%
  \begin{subfigure}[]{0.5\columnwidth}\caption{}\includegraphics[width=\columnwidth]{../../plots/bothbound_stroke_taily_positions}\end{subfigure}\\
  \begin{subfigure}[]{0.5\columnwidth}\caption{}\includegraphics[width=\columnwidth]{../../plots/bothbound_long_stroke_angles_bd}\end{subfigure}
  \caption{\textbf{Dynein model exhibits powerstroke, not winch, dynamics.} \textit{A. left: } Schematic of the winch mechanism. On free MTBD binding, linker swing in the just-bound head pulls the tail and cargo in the direction of the just-bound MTBD. \textit{A. right: } Schematic of the powerstroke mechanism. On free MTBD binding, linker swing pushes the just-bound head and tail domains towards the minus-end of the MT and alters the just-bound stalk domain's angle with the MT. Data used for subfigures b-e are for all steps with a positive step size. \textit{b.) } Just-bound MTBD stalk angle relative to MT axis as a function of time since MTBD binding along with MTBD angle equilibrium (blue dotted line). \textit{c.) } Just-bound head angle, along with prestroke equilibrium (red dotted line) and poststroke equilibrium (blue dotted line). \textit{d.) } Change in tail domain x coordinate since MTBD binding. \textit{e.) } Value of tail domain y coordinate. All values sampled every $10 ns$. \textit{f.) } Just-bound MTBD stalk angle over the entirety of the post-powerstroke state, sampled every 1 $\mu s$. All values plotted as mean $\pm$ SD.}
\label{fig:stroke}
\end{figure}

>>>>

\begin{figure}[tbhp]
  \centering
  \begin{subfigure}[]{0.8\columnwidth}\caption{}\vspace{5pt}\includegraphics[width=\columnwidth]{figures/winch-powerstroke-cartoon}\end{subfigure}\vspace{10pt}\\
  \begin{subfigure}[]{0.5\columnwidth}\caption{}\includegraphics[width=\columnwidth]{../../plots/bothbound_stroke_angles_bd}\end{subfigure}%
  \begin{subfigure}[]{0.5\columnwidth}\caption{}\includegraphics[width=\columnwidth]{../../plots/bothbound_stroke_angles_md}\end{subfigure}\\
  \begin{subfigure}[]{0.5\columnwidth}\caption{}\includegraphics[width=\columnwidth]{../../plots/bothbound_stroke_tailx_positions}\end{subfigure}%
  \begin{subfigure}[]{0.5\columnwidth}\caption{}\includegraphics[width=\columnwidth]{../../plots/bothbound_stroke_taily_positions}\end{subfigure}\\
  \begin{subfigure}[]{0.5\columnwidth}\caption{}\includegraphics[width=\columnwidth]{../../plots/bothbound_long_stroke_angles_bd}\end{subfigure}
  \caption{\textbf{Dynein model exhibits powerstroke, not winch, dynamics.} \textit{A. left: } Schematic of winch model for dynamics during conformation changes associated with right monomer binding. On free MTBD binding, linker swing in the just-bound head pulls the tail and cargo in the direction of the just-bound MTBD. \textit{A. right: } Schematic of the powerstroke model for dynamics during during conformation changes associated with right monomer binding. On free MTBD binding, linker swing pushes the just-bound head and tail domains towards the minus-end of the MT and alters the just-bound stalk domain's angle with the MT. Subfigures b-e describe dynamics for the right monomer during post-binding conformation change; only data for steps with a positive step size is shown. \textit{b.) } Just-bound MTBD stalk angle relative to MT axis as a function of time since MTBD binding along with MTBD angle equilibrium (blue dotted line). \textit{c.) } Just-bound head angle, along with prestroke equilibrium (red dotted line) and poststroke equilibrium (blue dotted line). \textit{d.) } Change in tail domain x coordinate since MTBD binding. \textit{e.) } Value of tail domain y coordinate. All values sampled every $10 ns$. \textit{f.) } Just-bound MTBD stalk angle for the millisecond after binding, sampled every 20 $\mu s$. All values plotted as mean $\pm$ SD.}
\label{fig:stroke}
\end{figure}
